#Get the names of the column which are in spanish and replace them with the english equivalent

```{r}
colnames(data)=c("fecha_dato"="Date","ncodpers"="Id","ind_empleado"="Emp_status","pais_residencia"="Country","sexo"="Sex","age"="Age",
"fecha_alta"= "Date2", "ind_nuevo"="New_Customer", "antiguedad"="Seniority","indrel"="Primary_customer",
"ult_fec_cli_1t"="Pr_customer_ld", "indrel_1mes"="Customer_type", "tiprel_1mes"="Customer_st_end_m", "indresi"="Residency",
"indext"="Foreigner", "conyuemp"="emp_spouse", "canal_entrada"="Entry_chanal", "indfall"="Deceased", "tipodom"="Address_type",
"cod_prov"="Province_code",   "nomprov"="province_name", "ind_actividad_cliente"="Activity_st", "renta"="Household",
"segmento"="Segment", "ind_ahor_fin_ult1"="Savings", "ind_aval_fin_ult1"="Guarantees", "ind_cco_fin_ult1"="Current_Acc",
"ind_cder_fin_ult1"="Derivada", "ind_cno_fin_ult1"="Payroll_Acc", "ind_ctju_fin_ult1"="Junior_Acc", 
"ind_ctma_fin_ult1"="M_particular_Acc ",   "ind_ctop_fin_ult1"="Particular_Acc", "ind_ctpp_fin_ult1"="Particular_Plus_Acc",
"ind_deco_fin_ult1"="Short_term_dep", "ind_deme_fin_ult1"="Medium_term_dep",  "ind_dela_fin_ult1"="Long_term_dep",
"ind_ecue_fin_ult1"="e-account", "ind_fond_fin_ult1"="Funds", "ind_hip_fin_ult1" = "Mortgage", "ind_plan_fin_ult1"="Pensions_Acc",
"ind_pres_fin_ult1"= "Loans", "ind_reca_fin_ult1"="Taxes", "ind_tjcr_fin_ult1"="Credit_Card", "ind_valo_fin_ult1"="Securities",
"ind_viv_fin_ult1"="Home_Acc", "ind_nomina_ult1"="Payroll", "ind_nom_pens_ult1"="Pensions", "ind_recibo_ult1"="Direct_Debit")
```

#As the database is very large we will look at 3 monthw of data from October 2015 untill December 2015
#to predict what products should be recommended to active customers
```{r}
train.data<-subset(data, data$Date=="2015-10-28"|data$Date=="2015-11-28"|data$Date=="2015-12-28")
```

#Explore the structure of the data frame to understand the attributes, the class of the atributes
```{r}
head(train.data)
str(train.data)
```

#Check how many unique cutomers are there in the database. 
#The second column hold the identification numbers for the customers
```{r}
length(unique(data[,2]))
```

#Check HOW many missing values are in the dataframe for each attribute
```{r}
sapply(train.data, function(x) sum(is.na(x)))
```

#Replace missing value of Household income with the mean household income of the customer's province .
```{r}
clean_data<-impute_proxy(train.data, Household ~ mean(Household,na.rm=TRUE) | province_name)
```

#Province_code has a 3992  missing values, but the column is not needed because the same information is provided by province_name, as a result the Province_code column will be removed
```{r}
clean_data<-clean_data[-20]
```


All the missing value were replaced with the approprite values, but there are some empty spaces for different variables, which need to be replaced. Emp_spouse has the value of "S" if the customer is the spouse of an employee and "N" otherwise. We notice that out of 2.710.381 observations, we have only 3 entry for S and 341 for N. The rest are blank spaces. In conclusion, the variable emp_spouse doesn't offer a lot of information and the entire column will be removed.

```{r}
#emp_spouce with value S
length(clean_data$emp_spouse[clean_data$emp_spouse=="S"])
#emp_spouce with value N"
length(clean_data$emp_spouse[clean_data$emp_spouse=="N"])
#blank spaces in  emp_spouce
length(clean_data$emp_spouse[clean_data$emp_spouse==""])

clean_data<-clean_data[-16]

```
Sex column has 15 empty spaces and they will be replaced with the most comun value
```{r}
#Number of blank space in Sex Column
length(clean_data$Sex[clean_data$Sex==""])
# creating a function to calculate the mode
calculate_mode<-function(x){
  uniq<-unique(na.omit(x))
  uniq[which.max(tabulate(match(x,uniq)))]
}
clean_data$Sex[clean_data$Sex==""]<-calculate_mode(clean_data$Sex)
```
Pr_customer_ld has 2703492 empty space, as a result the column will be removed( as most of the cells were empty)
```{r}

length(clean_data$Pr_customer_ld[clean_data$Pr_customer_ld==""])
#remove the Pr_customer_ld column
clean_data<-clean_data[-11]
```

The Customer_type column should have the following values:1,2,3,4 and P. We will replace 1.0 with 1, 2.0 with 2, 3.0 with 3 and 4.0 with 4, P with a value of 5 and the empty spaces will be replaced with the most comun value. 
```{r}
length(clean_data$Customer_type[clean_data$Customer_type==""])
unique(clean_data$Customer_type)
clean_data$Customer_type[clean_data$Customer_type=="P"]<-5
clean_data$Customer_type[clean_data$Customer_type=="1.0"]<-1
clean_data$Customer_type[clean_data$Customer_type=="2.0"]<-2
clean_data$Customer_type[clean_data$Customer_type=="3.0"]<-3
clean_data$Customer_type[clean_data$Customer_type=="4.0"]<-4
clean_data$Customer_type[clean_data$Customer_type==""]<-calculate_mode(clean_data$Customer_type)
clean_data$Customer_type<-as.factor(clean_data$Customer_type)
```

The 47325 empty spaces in Customer_st_end_m will be replaced as well as the most comun value
```{r}
#nr of blank spaces in Customer_st_end_m
length(clean_data$Customer_st_end_m[clean_data$Customer_st_end_m==""])
#impoute the most comun value
clean_data$Customer_st_end_m[clean_data$Customer_st_end_m==""]<-calculate_mode(clean_data$Customer_st_end_m)

```

  The Entry_chanal variable has 58.026 blank spaces. They will be replaced with the most frequent value that occurs in the case of females and then we will do the same thing for males
```{r}
length(clean_data$Entry_chanal[clean_data$Entry_chanal==""])
Entry_chanal_female=calculate_mode(clean_data$Entry_chanal[grepl("V",clean_data$Sex)])
clean_data$Entry_chanal[grepl("V",clean_data$Sex) & clean_data$Entry_chanal==""]=Entry_chanal_female

Entry_chanal_male=calculate_mode(clean_data$Entry_chanal[grepl("H",clean_data$Sex)])
clean_data$Entry_chanal[grepl("H",clean_data$Sex) & clean_data$Entry_chanal==""]=Entry_chanal_male

rm(Entry_chanal_female, Entry_chanal_male)
```

  The blank spaces in segment variable will be considered as different segment that it will be named "Other"
```{r}
length(clean_data$Segment[clean_data$Segment==""])
clean_data$Segment[clean_data$Segment==""]<-"Other"
```

  The province_name variable has 11.932 blank spaces. After further investigation we notice that the customers for whom the province_name is blank,  19 of them are from Spain and the most comun value will be imputed and the rest come from other countries than Spain. We will impute the value "International" for the blank spaces in this case.
```{r} 
#Number of observation with blank space in the province_name column"
length(clean_data$province_name[clean_data$province_name==""])

#The country of the customers with blank space in the province_name column"
unique(clean_data$Country[clean_data$province_name==""])

#Customers with blank space in the province_name column from Spain"
length(clean_data$province_name[clean_data$province_name==""& clean_data$Country=="ES"])

clean_data$province_name[clean_data$province_name==""& clean_data$Country=="ES"]<-calculate_mode(clean_data$province_name)

clean_data$province_name[clean_data$province_name==""]<-"International"

```

 Date2, the date at which the individual became a customer of the bank is not needed as the same information is reflected in the Seniority(months)= the difference between Date and Date 2

```{r}
clean_data<-clean_data[-7]
```


  The purpose of recommender system is to recommend new products to the active customers.As a result, inactive and deceased customers will be removed
```{r}
#subsetting just the customers who are active
clean_data<-subset(clean_data, clean_data$Activity_st=="1")
#subsetting just the customers who are not deceased
clean_data<-subset(clean_data, clean_data$Deceased=="N")

```

